\thesistitle

### 2019-07-16 sections/clonerefactor.tex
Removing redundant clone classes conceptually

>>>>

\subsubsection{Removing redundant clone classes}
Using the method described in the this section, we do find redundant clones. We remove these clones if they are a subset of an existant clone. We define the subset relation between clones as displayed as follows:

\begin{equation}\label{eq:subset}
C_1\text{ is a subset of }C_2\text{ \textit{iff} } \forall (i_1 \in C_1) \text{ } \exists (i_2 \in C_2) \text{ } F i_1 = F i_2 \wedge R i_1 \subseteq R i_2
\end{equation}

where \textit{C} refers to a clone class (a set of clone instances), \textit{i} refers to a clone instance, \textit{F} in which a clone instance is found and \textit{R} is the range of tokens that a clone instance spans.
